Model Search in Relational Domains

### 2016-10-21 paper.tex
abstract

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalization
of the well-known Conflict-Driven Clause Learning (CDCL) algorithm that is
used in SAT solvers.  ACDCL alternates between a model search, which
performs overapproximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in satisfiability 
solvers can be rather easily lifted from the boolean lattice to other 
non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial adaptations of the model search
and conflict analysis algorithms in ACDCL in order to enable the use of
relational abstract domains.  We have implemented these algorithms inside
the 2LS verification tool and instantiated our analysis over a template
polyhedra domain.  We evaluate the performance of our analyzer in comparison
with program verifiers that uses propositional-level solvers and a static
analysis tool.
%
Experimental evidence on a set of benchmarks drawn from bit-vector
regression in SV-COMP'16, bit-precise software models of hardware circuits
auto-generated from v2c tool, and several bounds checking benchmarks shows
significant reduction in the number of decisions and backjumping iterations
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
%
\end{abstract}

>>>>

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalization
of the well-known Conflict-Driven Clause Learning (CDCL) algorithm that is
used in SAT solvers.  ACDCL alternates between a model search, which
performs overapproximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
%
ACDCL has been successfully used with non-relational abstract domains such
as intervals to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning used in satisfiability 
solvers can be rather easily lifted from the boolean lattice to other 
non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions.
%
In this paper, we present the non-trivial adaptations of the model search
and conflict analysis algorithms in order to enable the use of
relational abstract domains.  We have implemented these algorithms inside
the 2LS verification tool and instantiated our analyzer over a template 
polyhedra domain to check safety properties of C programs.  We evaluate 
the performance of our analyzer in comparison with program verifiers that 
uses propositional-level solvers and a static analysis tool.
%
Experimental evidence suggest 
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
two orders of magnitude reduction in the number of 
decisions and conflict analysis compared to a satisfiability 
solver while being more precise compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}
